Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-23 prop_iop.tex
prop_iop.tex \subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule} Added...

\subsubsection{Convex and Finite Number of Intervals in Low Dimension}

@@

\begin{proof}~
\begin{itemize}
\item Since $c\left(x\right)\le x$, $0\le x-c\left(x\right)$. Also, $c\left(x\right)=c\left(1-x\right)\le1-x$
implies $x+c\left(x\right)\le1$. Therefore, $\iota_{c}'\left(x\right)=\left[x-c\left(x\right),x+c\left(x\right)\right]\subseteq\left[0,1\right]$.
\item For any $x\in\left[0,1\right]$, $\iota_{c}'\left(1-x\right)=\left[1,1\right]-\left[x-c\left(1-x\right),x+c\left(1-x\right)\right]=\left[1,1\right]-\iota_{c}'\left(x\right)$.
\item Since $c\left(0\right)\in\left[0,1\right]$ and $c\left(0\right)\le0$,
we have $c\left(0\right)=0$. Therefore, $\iota_{c}'\left(0\right)=\left[0,0\right]$,
and $\iota_{c}'\left(1\right)=\left[1,1\right]-\iota_{c}'\left(0\right)=\left[1,1\right]$. 
\item Given any three numbers\nb$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$,
if $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, we have
\begin{equation}\eqalign{ 
 & c\left(x_{0}+x_{1}+x_{2}\right)+c\left(x_{2}\right)\le c\left(x_{0}+x_{2}\right)+c\left(x_{1}+x_{2}\right)\\
\Rightarrow & \left[x_{0}+x_{1}+x_{2}+c\left(x_{0}+x_{1}+x_{2}\right)\right]+\left[x_{2}+c\left(x_{2}\right)\right]\\
 & \le\left[x_{0}+x_{2}+c\left(x_{0}+x_{2}\right)\right]+\left[x_{1}+x_{2}+c\left(x_{1}+x_{2}\right)\right]\,. }\end{equation}
Also, 
\begin{equation}\eqalign{ 
 & c\left(x_{0}+x_{1}+x_{2}\right)+c\left(x_{2}\right)\le c\left(x_{0}+x_{2}\right)+c\left(x_{1}+x_{2}\right)\\
\Rightarrow & -c\left(x_{0}+x_{2}\right)-c\left(x_{1}+x_{2}\right)\le-c\left(x_{0}+x_{1}+x_{2}\right)-c\left(x_{2}\right)\\
\Rightarrow & \left[x_{0}+x_{2}-c\left(x_{0}+x_{2}\right)\right]+\left[x_{1}+x_{2}-c\left(x_{1}+x_{2}\right)\right]\\
 & \le\left[x_{0}+x_{1}+x_{2}-c\left(x_{0}+x_{1}+x_{2}\right)\right]+\left[x_{2}-c\left(x_{2}\right)\right]\,. 
}\end{equation}
The above two equations implies $\iota_{c}'\left(x_{0}+x_{1}+x_{2}\right)+\iota_{c}'\left(x_{2}\right)\subseteq\iota_{c}'\left(x_{0}+x_{2}\right)+\iota_{c}'\left(x_{1}+x_{2}\right)$.
\item For a set\nb$\left\{ x_{i}\right\} _{i=1}^{N}\subseteq\left[0,1\right]$,
if $\sum_{i=1}^{N}x_{i}\in\left[0,1\right]$, then $\iota_{c}'\left(\sum_{i=1}^{N}x_{i}\right)\subseteq\sum_{i=1}^{N}\iota_{c}'\left(x_{i}\right)$
by inducting on the convex condition listed previously with $x_{2}=0$.
\end{itemize}
\end{proof}

>>>>

@@

\begin{proof}~
\begin{itemize}
\item Since $c\left(x\right)\le x$, $0\le x-c\left(x\right)$. Also, $c\left(x\right)=c\left(1-x\right)\le1-x$
implies $x+c\left(x\right)\le1$. Therefore, $\iota_{c}'\left(x\right)=\left[x-c\left(x\right),x+c\left(x\right)\right]\subseteq\left[0,1\right]$.
\item For any $x\in\left[0,1\right]$, $\iota_{c}'\left(1-x\right)=\left[1,1\right]-\left[x-c\left(1-x\right),x+c\left(1-x\right)\right]=\left[1,1\right]-\iota_{c}'\left(x\right)$.
\item Since $c\left(0\right)\in\left[0,1\right]$ and $c\left(0\right)\le0$,
we have $c\left(0\right)=0$. Therefore, $\iota_{c}'\left(0\right)=\left[0,0\right]$,
and $\iota_{c}'\left(1\right)=\left[1,1\right]-\iota_{c}'\left(0\right)=\left[1,1\right]$. 
\item Given any three numbers\nb$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$,
if $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, we have
\begin{equation}\eqalign{ 
 & c\left(x_{0}+x_{1}+x_{2}\right)+c\left(x_{2}\right)\le c\left(x_{0}+x_{2}\right)+c\left(x_{1}+x_{2}\right)\\
\Rightarrow & \left[x_{0}+x_{1}+x_{2}+c\left(x_{0}+x_{1}+x_{2}\right)\right]+\left[x_{2}+c\left(x_{2}\right)\right]\\
 & \le\left[x_{0}+x_{2}+c\left(x_{0}+x_{2}\right)\right]+\left[x_{1}+x_{2}+c\left(x_{1}+x_{2}\right)\right]\textrm{ .} }\end{equation}
Also, 
\begin{equation}\eqalign{ 
 & c\left(x_{0}+x_{1}+x_{2}\right)+c\left(x_{2}\right)\le c\left(x_{0}+x_{2}\right)+c\left(x_{1}+x_{2}\right)\\
\Rightarrow & -c\left(x_{0}+x_{2}\right)-c\left(x_{1}+x_{2}\right)\le-c\left(x_{0}+x_{1}+x_{2}\right)-c\left(x_{2}\right)\\
\Rightarrow & \left[x_{0}+x_{2}-c\left(x_{0}+x_{2}\right)\right]+\left[x_{1}+x_{2}-c\left(x_{1}+x_{2}\right)\right]\\
 & \le\left[x_{0}+x_{1}+x_{2}-c\left(x_{0}+x_{1}+x_{2}\right)\right]+\left[x_{2}-c\left(x_{2}\right)\right]\textrm{ .} 
}\end{equation}
The above two equations implies $\iota_{c}'\left(x_{0}+x_{1}+x_{2}\right)+\iota_{c}'\left(x_{2}\right)\subseteq\iota_{c}'\left(x_{0}+x_{2}\right)+\iota_{c}'\left(x_{1}+x_{2}\right)$.
\item For a set\nb$\left\{ x_{i}\right\} _{i=1}^{N}\subseteq\left[0,1\right]$,
if $\sum_{i=1}^{N}x_{i}\in\left[0,1\right]$, then $\iota_{c}'\left(\sum_{i=1}^{N}x_{i}\right)\subseteq\sum_{i=1}^{N}\iota_{c}'\left(x_{i}\right)$
by inducting on the convex condition listed previously with $x_{2}=0$.
\end{itemize}
\end{proof}

\subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule}

Since we want to consider QIVPMs induced by the Born rule, it is easier
to work with the states instead of the probability measures, which
gives us the following definition.

\begin{definition}A state\nb$\rho$ is consistent with $\bar{\mu}$
on a projector\nb$P$ if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
i.e., $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{\left\{ P\right\} }\right)$,
and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$
is consistent with $\bar{\mu}$ on every projector in $S$, i.e.,
$\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu}|_{S}\right)$.\end{definition}
